Baseline centering problem

### 2018-12-19 paper/tangotd.tex

We should find a way to initialize $Z$ so that $Z\approx \Id$ at time
$0$, namely $Z(s,s)=1/\rho(s)$, although starting with $Z(s,s)=1$ should be
quite fine. (Small initializations of $Z$ are safer.) $Z>0$ (unless we work with $\gamma=1$ and relative stuff
TODO), so the parameterization could reflect that.

@@

Newton has a potential to be numerically less stable: first because of
the $(1+\eta)$ factor which makes $Z$ quickly grow when it's small (until
the $-Z^2$ kicks in), then because of the $-Z^2$ factors which can be
problematic when $Z$ is large. Small enough learning rates should be
stable.

@@

>>>>

We should find a way to initialize $Z$ so that $Z\approx \Id$ at time
$0$, namely $Z(s,s)=1/\rho(s)$, although starting with $Z(s,s)=1$ should be
quite fine. (Small initializations of $Z$ are safer.) $Z>0$ (unless we
work with $\gamma=1$ and relative stuff), so the parameterization should
reflect that. Indeed the Newton iteration is unstable with negative
values.

@@

Newton has a potential to be numerically less stable: first because of
the $(1+\eta)$ factor which makes $Z$ quickly grow when it's small (until
the $-Z^2$ kicks in), then because of the $-Z^2$ factors which can be
problematic when $Z$ is large. Small enough learning rates should be
stable. (TODO NOT TRUE: even in 1d, Newton is unstable if initialized to
a negative number, for any learning rate. Stable only in some
neighborhood of the true solution, but then, the stochastic noise might
produce divergence...)

@@

[TODO: Since the standard iteration is unstable for $Z<0$, this means the
iteration on $Z_0$ will be unstable for $Z_0<-\frac{1}{1-\gamma}$.
Use that somehow: clip at that value?]
